Sticks and tpos might help me

### 2020-12-29 paper/paper.tex
fix: smaller bugfixes in example and writing cleanup

    \begin{equation*}
        r_{\alpha}(010) = 010^{-}, 010 \in [\neg\alpha]
    \end{equation*}
    \begin{equation*}
        r_{\alpha}(110) = 110^{+}, 110 \in [\alpha]
    \end{equation*}

    and, as $r_{\alpha}(110^{+}) \prec r_{\alpha}(010^{-})$ is true, set $110 <_{\alpha}^{\ast} 010$.

@@

The operator $\ast$, based on $\preceq$, allows the revision of a tpo $\leq$ associated with an epistemic state to $\leq_{\alpha}^{\ast}$. To be used in iterated belief revision the newly introduced structure $\preceq$ also needs to be revised Otherwise, as Booth and Meyer put it, the problem has just "re-emerged 'one level up'" \cite{Booth2011}. In their paper they discuss strict preference hierarchies (or SPHs), an equivalent structure to $\preceq$ denoted as $\$$, their properties and how to revise them.

This report focuses on revision of tpos itself. As an outlook, only the revision of a $\leq$-faithful tpo $\preceq$ using the example operator from the original paper is included. For a more detailed explanation of the operator, SPHs or their properties see \cite{Booth2011}.

\subsection{A concrete operator}
Booth and Meyer define their operator to revise $\preceq$ by with a function $p: W^{\pm} \mapsto \mathds{R}$ so that for all $x \in W$ the interval between it's positive and negative representation $a$ is:

@@

Using $p$ a $\leq$-faithful tpo $\preceq_{p}$ satisfying \ref{PREQ1}-\ref{PREQ4} is defined by:

@@

Revision of $\preceq$ becomes a two step process: First choose a function $p$ so that $\preceq_{p} = \preceq$, then revise to get a new assignment $p \ast \alpha$ that defines a new $\leq$-faithful tpo $\preceq_{p \ast \alpha}$.

% TODO: probably don't need geffner ref here
Booth and Meyer suggest an operator that keeps worlds that satisfy $\alpha$ constant and moves $\neg\alpha$-worlds "back" by $a$ (also known as L-conditionalisation in Spohn-type rankings \cite{Geffner1992}). They achieve this by setting $p$, for every $x^{\epsilon} \in W^{\pm}$ to:

>>>>

    \begin{equation*}
        010 \in [\neg\alpha] \textrm{ : } r_{\alpha}(010) = 010^{-}
    \end{equation*}
    \begin{equation*}
        110 \in [\alpha] \textrm{ : } r_{\alpha}(110) = 110^{+}
    \end{equation*}

    and, as $110^{+} \prec 010^{-}$ is true, set $110 <_{\alpha}^{\ast} 010$.

@@

The operator $\ast$, based on $\preceq$, allows the revision of a tpo $\leq$ associated with an epistemic state to $\leq_{\alpha}^{\ast}$. To be used in iterated belief revision the newly introduced structure $\preceq$ also needs to be revised Otherwise, as Booth and Meyer put it, the problem has just "re-emerged 'one level up'" \cite{Booth2011}. In their paper they discuss strict preference hierarchies (or SPHs), an equivalent structure to $\preceq$, denoted as $\$$, their properties and how to revise them.

This report focuses on revision of tpos itself. As an outlook, only the revision of a $\leq$-faithful tpo $\preceq$ using the example operator from the original paper is included here. For a more detailed explanation of the operator, SPHs or their properties see \cite{Booth2011}.

\subsection{A concrete operator}
Booth and Meyer define their operator to revise $\preceq$ with a function $p: W^{\pm} \mapsto \mathds{R}$ so that for all $x \in W$ the interval between it's positive and negative representation is a real number $a$:

@@

Using $p$, a $\leq$-faithful tpo $\preceq_{p}$ satisfying \ref{PREQ1}-\ref{PREQ4} can be defined as:

@@

Revision of $\preceq$ becomes a two step process: First choose a function $p$ so that $\preceq_{p} = \preceq$, then revise $p$ to get a new assignment $p \ast \alpha$ that defines a new $\leq$-faithful tpo $\preceq_{p \ast \alpha}$.

% TODO: probably don't need geffner ref here
Booth and Meyer suggest an operator that keeps worlds that satisfy $\alpha$ constant and moves $\neg\alpha$-worlds "back" by $a$ (also known as L-conditionalisation in Spohn-type rankings \cite{Geffner1992}). They also mention other operators are possible and an area of further research. They achieve this by setting $p$, for every $x^{\epsilon} \in W^{\pm}$ to:
